---
title: "Airbnb_8"
output: html_document
---

```{r load_packages, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(mosaic)
library(ggfortify)
library(moderndive)
library(janitor)
library(huxtable)
library(here)
library(broom)
library(skimr)
library(GGally)
library(car)
library(vroom)
```

price = cost per night

cleaning_fee: cleaning fee

extra_people: charge for having more than 1 person

property_type: type of accommodation (House, Apartment, etc.)

room_type:

Entire home/apt (guests have entire place to themselves)
Private room (Guests have private room to sleep, all other rooms shared)
Shared room (Guests sleep in room shared with others)
number_of_reviews: Total number of reviews for the listing

review_scores_rating: Average review score (0 - 100)

longitude , latitude: geographical coordinates to help us locate the listing

neighbourhood*: three variables on a few major neighbourhoods in each city

```{r cars}
listings <- vroom("http://data.insideairbnb.com/denmark/hovedstaden/copenhagen/2020-06-26/data/listings.csv.gz") %>% 
    clean_names()  #get the listings for Copenhagen
```



```{r}
glimpse(listings) # Looking at the raw values
skim(listings) #Computing summary statistics of the variables of interest, or finding NAs
```



```{r  echo=FALSE}
listings$price = as.numeric(gsub("[\\$,]", "", listings$price)) # make price into a numeric variable
listings$cleaning_fee = as.numeric(gsub("[\\$,]", "", listings$cleaning_fee))

skim(listings) #check if all the variables are in the correct type
```


